Long range correlations and their event scale dependence in high multiplicity pp collisions at $\sqrt{s} = 13$~TeV

### 2020-06-18 sec_ana.tex
add refereces and update on ana

The ridge yield is further studied with respect to, so called event scale. Usually event scale the momentum of the hard process. Events with the hard process are selected by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering. The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle. Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$. Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle. The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured for the $k_{\rm{T}}$ algorithm with $R = 0.2$.

>>>>

The ridge yield is further studied by exploiting the momentum transfer between the interacting partons, so called, event scale. On average, increasingly hard parton interactions result from pp collisions with decreasing impact parameters between the two protons~\cite{Sjostrand:1986ep,Frankfurt:2010ea}.
In this article, the event scales are set by requiring minimum transverse momentum of leading track or jet reconstruction in mid-rapidity since leading tracks with a high $p_\mathrm{T}$ or jets result from the hard scattering. The leading track is selected within $|\eta|<0.9$ and the full azimuthal angle. Jets are reconstructed with charged particles only (charged jets) for the anti-$k_{\rm{T}}$ algorithm and the resolution parameter $R = 0.4$. Jets are selected in $|\eta_\mathrm{jet}|<0.4$ and the full azimuthal angle. The transverse momentum of jets $p_\mathrm{T,\,jet}$ is corrected for underlying event density that is measured for the $k_{\rm{T}}$ algorithm with $R = 0.2$.
